Covariate analysis of UFL-Mayo-ISB RNASeq reprocessed counts (both cerebellum and temporal cortex)

### 2016-06-02 code/Rmd/Mayo_RNASeq_Reprocessed.Rmd
Minor modifications

# library(doParallel)
# library(foreach)
# 
# cl = makeCluster(14)
# registerDoParallel(cl)

@@

```{r summary, results='asis', echo=FALSE}
writeLines('Number of samples in each category are')
tmp = data.frame(summary(COVARIATES$BrainRegion.Diagnosis))
colnames(tmp) = "No. of samples"
kable(tmp)
```

@@

@@

# Store differential expression results
write.table(DE, file = 'MAYOdiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MAYOdiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
stopCluster(cl)
```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r COV_OBJ$properties$id`      |
|  Raw counts (logCPM)      |  `r RAWCPM_OBJ$properties$id`   |
|  Residual Expression      |  `r EXP_OBJ$properties$id`      |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`     |

>>>>

library(doParallel)
library(foreach)

cl = makeCluster(2)
registerDoParallel(cl)

@@

```{r summary, results='asis', echo=FALSE}
writeLines('Number of samples in each category are')
tmp = summary(COVARIATES$BrainRegion.Diagnosis) %>%
  rownameToFirstColumn('SampleName') %>%
  tidyr::separate(SampleName, c('BrainRegion','Diagnosis'), sep = '\\.') %>%
  tidyr::spread(Diagnosis, DF)
kable(tmp)
```

@@

# Design Matrix
write.table(DM1$design, file='MAYOdesign.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('MAYOdesign.tsv', 
                  name = 'Design Matrix',
                  parentId = CODE$properties$id)
DM_OBJ = synStore(DM_OBJ,
                      used = ALL_USED_IDs, 
                      activityName = activityName, 
                      executed = thisFile, 
                      activityDescription = activityDescription)

@@

# Store differential expression results
write.table(DE, file = 'MAYOdiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MAYOdiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
stopCluster(cl)
```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r COV_OBJ$properties$id`      |
|  Raw counts (logCPM)      |  `r RAWCPM_OBJ$properties$id`   |
|  Design Matrix            |  `r DM_OBJ$properties$id`       |
|  Residual Expression      |  `r EXP_OBJ$properties$id`      |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`     |
